% ====================
% EXPERIENCE A
% ====================
\subsection{{Software Development Intern \hfill Sept 2024 --- Present}}
\subtext{\href{https://codemonk.io/}{Codemonk}\hfill Bengaluru - Remote}
\begin{zitemize}
\item  Building  \href{https://www.chessbook.in/}{\textbf{Chessbook.in}}  using \textbf{Next.js}, 
 NextAuth.js, and Chess.js, Node.js, Express.js, with \textbf{Firebase} and \textbf{Socket.IO} for\textbf{ real-time} data management with an average  retention of \textbf{5 games played per user per week}..
\item Implemented secure authentication and server-side logic using \textbf{Node.js} and \textbf{Express} for a seamless \textbf{multiplayer} experience.
\end{zitemize}

% ====================
% EXPERIENCE B
% ====================
\subsection{{Full Stack Development Intern \hfill Sept 2023 --- Present}}
\subtext{\href{https://targettechnology.in/links}{TargetTech}\hfill Kolkata – Remote}
\begin{zitemize}
\item Designed and developed Front-end and Back-end of of Various projects using Next.js and Tailwind CSS, MongoDB,
Express.js,\textbf{  AWS-S3},\textbf{ Sanity}, \textbf{Strapi} and many more, resulting in a seamless user experience.
\item Built \href{https://www.codehelp.in/devchallenge/dashboard}{\textbf{DevChallenges}} \href{https://www.codehelp.in/devchallenge/dashboard}{\textbf{QuickCompiler}} an online compiler for HTML, CSS, JavaScript Practice End-to-End.
\item  Worked on \href{https://www.codehelp.in/}{\textbf{CodeHelp}}, \href{https://ppf-guide.tintandorange.com/}{\textbf{Tint&Orangend }} and many more projects.
\end{zitemize}

% ====================
% EXPERIENCE C
% ====================
\subsection{{Software Development Intern\hfill July 2024 --- Sept 2024}}
\subtext{\href{https://www.endlessriver.ai/}{EndlessRiver.ai} \hfill Bengaluru - Remote}
\begin{zitemize}
\item Developed \textbf{intelligent bot} solutions for \textbf{Microsoft Teams} and \textbf{Slack} using Next.js and NextAuth for secure implementation. Specialized in seamless integrations across \textbf{Microsoft 365} ecosystems to streamline organizational processes.
\item Integrates \textbf{AI} and \textbf{Retrieval-Augmented Generation (RAG)} technologies to enhance bot capabilities, improving information retrieval and processing across organizational \textbf{workflows}.
\end{zitemize}

%====================
% EXPERIENCE D
%====================
\subsection{{\textbf{Software Development Intern }\hfill Jan 2024 --- July 2024}}
\subtext{\href{http://www.dair.cloud/}{Dair Cloud } \hfill Florida, USA}
\begin{zitemize}
\item Worked on the \href{https://cais.dair.cloud/login}{\textbf{Cais Manager}\textbf{ dashboard}}, implementing advanced data filtering features using\textbf{ Next.js, PrimeReact, }and
\textbf{PrimeFlex, }and leveraging\textbf{ ReactFlow, Camunda, Cube.js, and CloudDesign }for component development with\textbf{ Tailwind CSS } reducing data retrieval time by \textbf{30\%}, leading to faster decision-making for enterprise users.
\item Worked on \textbf{omni-control} another project of Dair, handling thousands of records using cube.js and \textbf{apache graph}.
\item \textbf{algorithms}. leveraging multiple alias matching algorithms to handle \textbf{data} in chunks.
\end{zitemize}
